---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sgstar

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/yogasatria30/sgstar.svg?branch=master)](https://travis-ci.com/yogasatria30/sgstar)
<!-- badges: end -->
A set of function that implementaion for seasonal spatio temporal analysis based on Seasonal Generalized Space-Time Autoregressive with Seemingly Unrelated Regression (S-GSTAR-SUR) Model by Setiawan et al.(2016)<Corpus ID: 189955959>.

## Installation

You can install the released version of sgstar from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("sgstar")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example sgstar}
library(sgstar)
#basic example code

data("coords")
data("simulatedata")

#create weight matrix using distance inverse matrix

z<-dist(coords,method = "euclidean")
z <- as.matrix(z)

matriksd <- 1/z
matriksd[is.infinite(matriksd)] <- 0

matriksd_w <- matriksd / rowSums(as.data.frame(matriksd))

fit <- sgstar(data = simulatedata, w = matriksd_w, p = 2,ps = 1, s =4)
fit
```

```{r example predict_sgstar}
#example for predict 
predict.fit <-predict_sgstar(fit,12)
predict.fit
```

```{r example plot_sgstar}
#example fo create plot
plot1 <- plot_sgstar(fit)
```




